[Re] Non-additive coupling enables propagation of synchronous spiking activity in purely random networks

### 2018-02-09 article/Caze_2018.tex
Readd accidentally deleted text

For linearly coupled networks, the neuron model is a standard leaky-integrate-and-fire neuron with ``delta synapses'', i.e. incoming synaptic events instantaneously affect the membrane potential as soon as they are received. In Brian, this model is described as follows (omitting the code to connect the synapses and set their weights):
\begin{code}
eq = "dV/dt = -gamma*V + V0 : volt"
G = br2.NeuronGroup(N, model=eq, threshold="V>Theta",
                    reset="V=0*mV", method='euler')
exc_syn = br2.Synapses(G, G, 'w : volt (constant, shared)',
                       on_pre='V += w', delay=5 * ms - dt)
inh_syn = br2.Synapses(G, G, 'w : volt (constant, shared)',
                       on_pre='V -= w', delay=5 * ms - dt)
\end{code}

Note that the delay has been set as one time step (\verb|dt|) less than \SI{5}{\milli\second}. This is because in Brian, when a neuron receives synaptic input, this input can only trigger a threshold crossing of the receiving neuron in the following time step. To get chains of propagated synchronous spikes every \SI{5}{\milli\second} as in the original study, we therefore have to reduce the delay by one time step.

For non-linearly coupled networks, we have to use a slightly more complicated approach where we sum up all the received excitatory input in a variable \verb|ve|, apply the non-linear function $\sigma$ to this input, and then reset the variable \verb|ve| back to 0 to prepare for the next time step. In Brian syntax (the definition of the inhibitory synapses is identical to the linearly-coupled network):
\begin{code}
eq = """dV/dt = -gamma*V + V0 : volt
        ve : volt
     """
G = br2.NeuronGroup(N, model=eq, threshold="V>Theta",
                    reset="V=0*mV", method='euler')
exc_syn = br2.Synapses(G, G, 'w : volt (constant, shared)',
                       on_pre='ve += w', delay=5 * ms - dt)
G.run_regularly('''
                V += clip(ve, 0*mV, 2*mV) + clip(2*(ve-2*mV), 0*mV, 4*mV)
                ve = 0*mV
                ''', when='after_synapses')
\end{code}
The \verb|run_regularly| operation that is run every time step to implement the non-linear $\sigma$ function refers to the predefined \verb|clip| function which clips the value to a given range, following the syntax
\begin{code}
clip(value, lower_bound, upper_bound)
\end{code}

To facilitate simulation, we use the \emph{joblib} library to automatically store results and to distribute computation over processor cores. Several simulation and analysis functions are annotated with a \verb|@mem.cache| decorator, meaning that their input arguments and outputs will be automatically stored to disk and calling the function will return the stored values if available. This feature does not only ease development (e.g. plotting functions can be changed without re-running the underlying simulations), but also allows to interrupt long-running parameter explorations without losing the results obtained so far. The same result could be achieved by manually storing results to disk, but joblib's caching mechanism helps to avoid common errors (e.g. to re-use an old result obtained with an outdated version of the code) while keeping the code readable. To reduce the total simulation time, the grid exploration in Fig.~\ref{fig:grid}, and the analysis of group size evolution in Fig.~\ref{fig:markov} have been distributed over processor cores using joblib's \verb|Parallel| construct. For the simulations presented in Fig.~\ref{fig:grid}, multiple repetitions for the same combination of synaptic weights are distributed over processor cores, for the simulations presented in Fig.~\ref{fig:markov}, simulations are evaluated in parallel over group sizes. In both cases, a number of $C-1$ parallel processes is used, where $C$ is the number of processor cores in the user's system.

>>>>

For linearly coupled networks, the neuron model is a standard leaky-integrate-and-fire neuron with ``delta synapses'', i.e. incoming synaptic events instantaneously affect the membrane potential as soon as they are received. In Brian, this model is described as follows (omitting the code to connect the synapses and set their weights):
\begin{code}
eq = "dV/dt = -gamma*V + V0 : volt"
G = br2.NeuronGroup(N, model=eq, threshold="V>Theta",
                    reset="V=0*mV", method='euler')
exc_syn = br2.Synapses(G, G, 'w : volt (constant, shared)',
                       on_pre='V += w', delay=5 * ms - dt)
inh_syn = br2.Synapses(G, G, 'w : volt (constant, shared)',
                       on_pre='V -= w', delay=5 * ms - dt)
\end{code}
Note that the delay has been set as one time step (\verb|dt|) less than \SI{5}{\milli\second}. This is because in Brian, when a neuron receives synaptic input, this input can only trigger a threshold crossing of the receiving neuron in the following time step. To get chains of propagated synchronous spikes every \SI{5}{\milli\second} as in the original study, we therefore have to reduce the delay by one time step.

For non-linearly coupled networks, we have to use a slightly more complicated approach where we sum up all the received excitatory input in a variable \verb|ve|, apply the non-linear function $\sigma$ to this input, and then reset the variable \verb|ve| back to 0 to prepare for the next time step. In Brian syntax (the definition of the inhibitory synapses is identical to the linearly coupled network):
\begin{code}
eq = """dV/dt = -gamma*V + V0 : volt
        ve : volt
     """
G = br2.NeuronGroup(N, model=eq, threshold="V>Theta",
                    reset="V=0*mV", method='euler')
exc_syn = br2.Synapses(G, G, 'w : volt (constant, shared)',
                       on_pre='ve += w', delay=5 * ms - dt)
G.run_regularly('''
                V += clip(ve, 0*mV, 2*mV) + clip(2*(ve-2*mV), 0*mV, 4*mV)
                ve = 0*mV
                ''', when='after_synapses')
\end{code}
The \verb|run_regularly| operation that is run every time step to implement the non-linear $\sigma$ function refers to the predefined \verb|clip| function which clips the value to a given range, following the syntax
\begin{code}
clip(value, lower_bound, upper_bound)
\end{code}
To facilitate simulation, we use the \emph{joblib} library to automatically store results and to distribute computation over processor cores. Several simulation and analysis functions are annotated with a \verb|@mem.cache| decorator, meaning that their input arguments and outputs will be automatically stored to disk and calling the function will return the stored values if available. This feature does not only ease development (e.g. plotting functions can be changed without re-running the underlying simulations), but also allows to interrupt long-running parameter explorations without losing the results obtained so far. The same result could be achieved by manually storing results to disk, but joblib's caching mechanism helps to avoid common errors (e.g. to re-use an old result obtained with an outdated version of the code) while keeping the code readable. To reduce the total simulation time, the grid exploration in Fig.~\ref{fig:grid}, and the analysis of group size evolution in Fig.~\ref{fig:markov} have been distributed over processor cores using joblib's \verb|Parallel| construct. For the simulations presented in Fig.~\ref{fig:grid}, multiple repetitions for the same combination of synaptic weights are distributed over processor cores, for the simulations presented in Fig.~\ref{fig:markov}, simulations are evaluated in parallel over group sizes. In both cases, a number of $C-1$ parallel processes is used, where $C$ is the number of processor cores in the user's system.
